Supplement to: Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-05-03 manuscripts/manuscript.Rmd
Increase replicate number and OptTime length

dt3 <- dt %>% 
  filter(replicate=="rep_17" & time < 20) %>%
  select(time, harvest, harvest_alt, penalty_fn) %>%
  gather(variable, value, -time, -penalty_fn)

@@

ggplot(filter(table1_long, reduction == 0.25),
  aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  scale_fill_discrete(name="error type") + 
  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
                              'L2' = substitute(paste(Pi[2])),
                              'fixed' = substitute(paste(Pi[3])))) + 
  xlab("Cost model") + 
  ylab(expression(NPV[0])) + theme_tufte(base_size=16)
write.csv(table1_long, "components/data/figure6.csv")
```

>>>>

dt3 <- dt %>% 
  filter(replicate=="rep_17" & time < OptTime) %>%
  select(time, harvest, harvest_alt, penalty_fn) %>%
  gather(variable, value, -time, -penalty_fn)

@@

ggplot(filter(table1_long, reduction == reduction),
  aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  scale_fill_discrete(name="error type") + 
  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
                              'L2' = substitute(paste(Pi[2])),
                              'fixed' = substitute(paste(Pi[3])))) + 
  xlab("Cost model") + 
  ylab(expression(NPV[0])) + theme_tufte(base_size=16)
write.csv(table1_long, "components/data/figure6.csv")
```

### 2015-05-03 manuscripts/supplement.Rmd
Increase replicate number and OptTime length

dt_s <- dt %>% 
  filter(replicate=="rep_17" & time < 20) %>%
  select(time, fishstock, alternate, penalty_fn) %>%
  gather(variable, value, -time, -penalty_fn)

@@

ex <- dt %>% 
  filter(replicate %in% paste0("rep_", 16:20) & time < 20) %>%
  select(time, fishstock, harvest, alternate, harvest_alt, replicate, penalty_fn) %>%
  gather(variable, stock, -time, -replicate, -penalty_fn)

@@

ex <- dt_quad %>% 
  filter(replicate=="rep_17" & time < 20) %>%
  select(time, harvest, harvest_alt) %>%
  gather(variable, stock, -time) 
ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=labels, 
                       name="")

@@

ggplot(filter(table2_long, reduction==0.25), 
  aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, scales="free_y") +
  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
  xlab("Penalty function")
write.csv(table2_long, "components/data/figureS7.csv")
```

>>>>

dt_s <- dt %>% 
  filter(replicate=="rep_17" & time < OptTime) %>%
  select(time, fishstock, alternate, penalty_fn) %>%
  gather(variable, value, -time, -penalty_fn)

@@

ex <- dt %>% 
  filter(replicate %in% paste0("rep_", 16:20) & time < OptTime) %>%
  select(time, fishstock, harvest, alternate, harvest_alt, replicate, penalty_fn) %>%
  gather(variable, stock, -time, -replicate, -penalty_fn)

@@

ex <- dt_quad %>% 
  filter(replicate=="rep_17" & time < OptTime) %>%
  select(time, harvest, harvest_alt) %>%
  gather(variable, stock, -time) 
ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=labels, 
                       name="")

@@

ggplot(filter(table2_long, reduction==reduction), 
  aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, scales="free_y") +
  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
  xlab("Penalty function")
write.csv(table2_long, "components/data/figureS7.csv")
```
